---
title: "CD Atlas: Dataset Loading, QC, and Pre-integration Merging"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(Seurat)
library(dplyr)
library(ggplot2)
library(readxl)
library(vroom)
library(Matrix)
```

# Overview

Loads and prepares all 9 CD datasets (P11–P19) for atlas integration.
Datasets originate from multiple sources and formats; each requires
source-specific ingestion and metadata harmonization before applying
unified per-dataset QC thresholds.

After QC, datasets are merged and saved for Harmony integration in
`01_cd_atlas_integration.R`.

```{r paths}
DATA_DIR   <- "/path/to/cd/scrna/data"
OUTPUT_DIR <- "/path/to/cd/scrna/output"
dir.create(file.path(OUTPUT_DIR, "merged_cd/plots"), showWarnings = FALSE, recursive = TRUE)
```

---

# 1. P11 – Ileocolonic CD multi-sample cohort (PM36206201)

29 GCA samples; each loaded from 10X Cellranger output and merged.

```{r p11-load}
load_10x_sample <- function(data_dir, patient_id, condition, tissue, disease_loc, treatment) {
  so <- CreateSeuratObject(counts = Read10X(data.dir = data_dir),
                           min.cells = 0, min.features = 0)
  so[["patient"]]          <- patient_id
  so[["source"]]           <- "P11"
  so[["condition"]]        <- condition
  so[["tissue_region"]]    <- tissue
  so[["disease_location"]] <- disease_loc
  so[["treatment"]]        <- treatment
  so[["percent.mt"]]       <- PercentageFeatureSet(so, pattern = "^MT-")
  so
}

# Example: GCA23 (Active, Ileum, Trt Naive)
# All 29 GCA samples follow this pattern and are loaded individually
gca_ids <- paste0("GCA", c(1:3,5,7:29))
gca_list <- lapply(gca_ids, function(id) {
  readRDS(file.path(DATA_DIR, paste0("PM36206201/data/GSE202052_RAW/", id, "/Seurat.RDS")))
})
p11 <- Reduce(merge, gca_list)
p11[["RNA"]] <- JoinLayers(p11[["RNA"]])

# Harmonize disease_location
p11_meta <- p11@meta.data %>%
  mutate(disease_location = case_when(disease_location == "Ileum" ~ "Ileal",
                                      TRUE ~ disease_location))
p11[["disease_location"]] <- p11_meta$disease_location
p11[["sample"]]           <- p11[["patient"]]
```

---

# 2. P12 – HC + CD multi-sample cohort (PM37495570)

12 samples (6 HC, 6 CD); each loaded from 10X Cellranger output.

```{r p12-load}
p12_samples <- list(
  HC_1 = list(patient = "P12_HC1",  condition = "Control",   tissue = "Colon (Sigmoid)", disease_loc = "None",         treatment = "None"),
  HC_2 = list(patient = "P12_HC2",  condition = "Control",   tissue = "Colon (Sigmoid)", disease_loc = "None",         treatment = "None"),
  HC_3 = list(patient = "P12_HC3",  condition = "Control",   tissue = "Colon (Sigmoid)", disease_loc = "None",         treatment = "None"),
  HC_4 = list(patient = "P12_HC4",  condition = "Control",   tissue = "Colon (Sigmoid)", disease_loc = "None",         treatment = "None"),
  HC_5 = list(patient = "P12_HC5",  condition = "Control",   tissue = "Colon (Sigmoid)", disease_loc = "None",         treatment = "None"),
  HC_6 = list(patient = "P12_HC6",  condition = "Control",   tissue = "Colon (Sigmoid)", disease_loc = "None",         treatment = "None"),
  CD_1 = list(patient = "P12_CD1",  condition = "Active",    tissue = "Colon (Sigmoid)", disease_loc = "Ileocolonic",  treatment = "Vedolizumab"),
  CD_2 = list(patient = "P12_CD2",  condition = "Active",    tissue = "Colon (Sigmoid)", disease_loc = "Ileocolonic",  treatment = "Vedolizumab"),
  CD_3 = list(patient = "P12_CD3",  condition = "Active",    tissue = "Colon (Sigmoid)", disease_loc = "Ileocolonic",  treatment = "Vedolizumab"),
  CD_4 = list(patient = "P12_CD4",  condition = "Active",    tissue = "Colon (Sigmoid)", disease_loc = "Ileocolonic",  treatment = "Vedolizumab"),
  CD_5 = list(patient = "P12_CD5",  condition = "Active",    tissue = "Colon (Sigmoid)", disease_loc = "Ileocolonic",  treatment = "Vedolizumab"),
  CD_6 = list(patient = "P12_CD6",  condition = "Inactive",  tissue = "Colon (Sigmoid)", disease_loc = "Ileocolonic",  treatment = "Vedolizumab")
)

p12_list <- lapply(names(p12_samples), function(sname) {
  readRDS(file.path(DATA_DIR, paste0("PM37495570/data/filtered/", sname, "/Seurat.RDS")))
})
p12 <- Reduce(merge, p12_list)
p12[["RNA"]] <- JoinLayers(p12[["RNA"]])

p12_meta <- p12@meta.data %>%
  mutate(disease_location = case_when(
    disease_location == "Ileum"  ~ "Ileal",
    disease_location == "Colon"  ~ "Colonic",
    TRUE ~ disease_location
  ))
p12[["disease_location"]] <- p12_meta$disease_location
p12[["sample"]]           <- p12[["patient"]]
```

---

# 3. P13 – Ileal CD cohort (PM31474370, Martin et al.)

Provided as a pre-processed RDS; metadata mapped from broad to atlas nomenclature.

```{r p13-load}
p13_raw <- readRDS(file.path(DATA_DIR, "PM31474370/data/Martin_All_Cells.rds"))
so       <- CreateSeuratObject(counts = p13_raw@assays$RNA@counts)
p13_meta <- p13_raw@meta.data %>%
  mutate(
    sample          = paste0("P13_", Sample_ID),
    patient         = paste0("P13_", Patient.ID),
    condition       = case_when(status == "Involved" ~ "Active", TRUE ~ "Inactive"),
    cell_category   = case_when(
      Broad_Annotation == "MNP"          ~ "Myeloid",
      Broad_Annotation == "B Cells"      ~ "B cells",
      Broad_Annotation == "T Cells"      ~ "T cells",
      Broad_Annotation == "Plasma Cells" ~ "Plasma cells",
      Broad_Annotation == "Stromal"      ~ "Mesenchymal",
      Broad_Annotation == "Proliferating"~ "Cycling"
    )
  )

so[["sample"]]          <- p13_meta$sample
so[["patient"]]         <- p13_meta$patient
so[["condition"]]       <- p13_meta$condition
so[["tissue_region"]]   <- "Ileum"
so[["disease_location"]]<- "Ileal"
so[["treatment"]]       <- "NA"
so[["cell_category"]]   <- p13_meta$cell_category
so[["cell_type"]]       <- p13_meta$Fine_Annotation
so[["percent.mt"]]      <- PercentageFeatureSet(so, pattern = "^MT-")
p13 <- so
```

---

# 4. P14 – HC + CD large cohort, colon and ileum (PM36720220)

Six tissue compartments (co_epi, co_imm, co_str, il_epi, il_imm, il_str) each
in Matrix Market format. Patient/condition/tissue metadata extracted from
supplementary Excel.

```{r p14-meta-load}
meta        <- read_excel(file.path(DATA_DIR, "PM36720220/data/1-s2.0-S1074761323000122-mmc2.xlsx"))
sample_meta <- read_excel(file.path(DATA_DIR, "PM36720220/data/1-s2.0-S1074761323000122-mmc2.xlsx"),
                          sheet = "Samples")

# Helper: extract patient and sample IDs from barcodes
extract_patient_id <- function(string) {
  string <- substr(string, 2, nchar(string))
  split_string <- strsplit(string, "_")[[1]]
  split_string[1]
}

format_sampleid <- function(string_vector) {
  modified <- vector("character", length = length(string_vector))
  for (i in seq_along(string_vector)) {
    if (grepl("_[A-Za-z]\\d+$", string_vector[i])) {
      modified[i] <- gsub("([A-Za-z])(\\d+)$", "\\2", string_vector[i])
    } else {
      modified[i] <- gsub("_[A-Za-z]$", "", string_vector[i])
    }
  }
  modified
}

load_p14_compartment <- function(mtx_dir) {
  raw      <- readMM(file.path(mtx_dir, list.files(mtx_dir, pattern = "\\.mtx$")))
  barcodes <- read.delim(file.path(mtx_dir, list.files(mtx_dir, pattern = "barcodes")),
                         header = FALSE)
  features <- read.delim(file.path(mtx_dir, list.files(mtx_dir, pattern = "features")),
                         header = FALSE)
  colnames(raw) <- barcodes$V1
  rownames(raw) <- features$V2
  df           <- CreateSeuratObject(counts = raw, min.cells = 0, min.features = 0)

  id_list      <- unlist(lapply(barcodes$V1, extract_patient_id))
  sample_list  <- unlist(lapply(barcodes$V1, function(x) strsplit(x, "-")[[1]][1]))
  mod_sample   <- format_sampleid(sample_list)
  source_ids   <- paste0("P14_", mod_sample)
  df[["patient"]] <- source_ids
  df[["source"]]  <- "P14"
  df[["patient_id2"]] <- id_list

  # Remove barcodes that can't be mapped to metadata
  df_meta <- df@meta.data %>%
    mutate(to_remove = ifelse(nchar(as.character(patient_id2)) < 3, 1, 0))
  df[["to_remove"]] <- df_meta$to_remove
  subset(df, subset = to_remove == 0)
}

# Match patient IDs to condition/disease/treatment
get_patient_meta <- function(id_list, meta_df) {
  lapply(id_list, function(id) {
    row <- which(meta_df$Donor.ID == id)
    list(condition = meta_df[[row, 6]],
         disease   = meta_df[[row, 4]],
         treatment = meta_df[[row, 12]])
  })
}

get_tissue_meta <- function(sample_list, meta_df) {
  lapply(sample_list, function(id) {
    row <- which(meta_df$Sample.ID == id)
    if (length(row) == 0) {
      prefix <- strsplit(id, "_")[[1]][1]
      row <- which(substr(meta_df$Sample.ID, 1, nchar(prefix)) == prefix)
    }
    if (length(row) > 0) meta_df[[row, 4]] else NA
  })
}
```

```{r p14-load}
compartment_dirs <- list(
  co_epi = file.path(DATA_DIR, "PM36720220/data/SCP1884/expression/colon_epi_raw"),
  co_imm = file.path(DATA_DIR, "PM36720220/data/SCP1884/expression/colon_imm_raw"),
  co_str = file.path(DATA_DIR, "PM36720220/data/SCP1884/expression/colon_stromal_raw"),
  il_epi = file.path(DATA_DIR, "PM36720220/data/SCP1884/expression/ileum_epi_raw"),
  il_imm = file.path(DATA_DIR, "PM36720220/data/SCP1884/expression/ileum_imm_raw"),
  il_str = file.path(DATA_DIR, "PM36720220/data/SCP1884/expression/ileum_stromal_raw")
)

p14_list <- lapply(compartment_dirs, load_p14_compartment)
p14 <- Reduce(merge, p14_list)
p14[["RNA"]] <- JoinLayers(p14[["RNA"]])
p14[["percent.mt"]] <- PercentageFeatureSet(p14, pattern = "^MT-")

# Attach condition/tissue from Excel metadata
id_list      <- as.vector(unlist(p14[["patient_id2"]]))
source_ids   <- as.vector(unlist(p14[["patient"]]))
mod_sample   <- gsub("^P14_", "", source_ids)

pmeta        <- get_patient_meta(id_list, meta)
tmeta        <- get_tissue_meta(mod_sample, sample_meta)

p14[["condition"]]       <- unlist(lapply(pmeta, `[[`, "condition"))
p14[["disease_location"]]<- unlist(lapply(pmeta, `[[`, "disease"))
p14[["treatment"]]       <- unlist(lapply(pmeta, `[[`, "treatment"))
p14[["tissue_region"]]   <- unlist(tmeta)
p14[["patient_id2"]]     <- NULL
p14[["to_remove"]]       <- NULL

# Harmonize patient IDs: strip barcode prefix to get numeric patient ID
p14[["sample"]]  <- p14[["patient"]]
p14_sample       <- as.vector(unlist(p14[["sample"]]))
p14[["patient"]] <- unlist(lapply(p14_sample, function(x) {
  parts <- strsplit(x, "_")[[1]]
  if (length(parts) == 1) paste0("P14_", substr(parts[1], 2, nchar(parts[1])))
  else                    paste0("P14_", substr(parts[2], 2, nchar(parts[2])))
}))
```

---

# 5. P15 – Ileal CD T-cell focused cohort (PM33771991)

9 samples (2 Control, 3 Active, 4 Inactive) from terminal ileum biopsies.

```{r p15-load}
p15_samples <- c("1425-1-ctrl", "1425-3-ctrl",
                  "1813-1-inf",  "1813-2-noninf", "1813-4-inf", "1813-6-noninf",
                  "1818-1-inf",  "1818-3-inf",    "1818-5-noninf")

p15_list <- lapply(p15_samples, function(s) {
  readRDS(file.path(DATA_DIR, paste0("PM33771991/data/filtered_gene_bc_matrices/", s, "/Seurat.RDS")))
})
p15 <- Reduce(merge, p15_list)
p15[["RNA"]]          <- JoinLayers(p15[["RNA"]])
p15[["cell_category"]]<- "T cells"

# Extract patient-level ID from sample field
p15[["sample"]]  <- p15[["patient"]]
p15_sample       <- as.vector(unlist(p15[["sample"]]))
p15[["patient"]] <- unlist(lapply(p15_sample, function(x) strsplit(x, "-")[[1]][1]))
```

---

# 6. P16 – Multi-region HC + CD cohort (PM34497389)

Raw count matrix and metadata preprocessed in Python and imported via CSV.

```{r p16-load}
count <- vroom(file.path(DATA_DIR, "PM34497389/data/raw_count_for_seurat.csv"))
meta  <- read.csv(file.path(DATA_DIR, "PM34497389/data/meta_for_seurat.csv"))

df <- as.data.frame(count)
rownames(df) <- df[, 1]; df <- df[, -1]
tdf <- data.frame(t(df))

p16 <- CreateSeuratObject(counts = tdf)
p16[["patient"]]          <- meta$patient
p16[["sample"]]           <- meta$sample
p16[["source"]]           <- "P16"
p16[["condition"]]        <- meta$condition
p16[["tissue_region"]]    <- meta$tissue_region
p16[["disease_location"]] <- meta$disease_location
p16[["treatment"]]        <- meta$treatment
p16[["cell_category"]]    <- meta$category
p16[["cell_type"]]        <- meta$Integrated_05
p16[["percent.mt"]]       <- PercentageFeatureSet(p16, pattern = "^MT-")
```

---

# 7. P17 – CD45+ sorted colon myeloid cohort (PM31730855)

5-prime expression matrix (Col1–6). Cells are pooled across 2–3 patients
per sequencing run; no per-patient disambiguation is possible.

```{r p17-load}
col16      <- read.delim(file.path(DATA_DIR, "PM31730855/data/raw/GSE121380_Col1-6_5prime_raw_gene_expression.txt"))
col16      <- as.data.frame(col16)
genes      <- col16[, 1]
col16      <- col16[, -1, drop = FALSE]
rownames(col16) <- genes

p17 <- CreateSeuratObject(col16, min.cells = 0, min.features = 0)

extract_patient_p17 <- function(input_string) {
  sample_num <- strsplit(input_string, ".", fixed = TRUE)[[1]][2]
  paste0("P17_", sample_num)
}
p17[["source"]]           <- "P17"
p17[["patient"]]          <- unlist(lapply(colnames(col16), extract_patient_p17))
p17[["sample"]]           <- p17[["patient"]]
p17[["condition"]]        <- "Control"
p17[["tissue_region"]]    <- "Colon"
p17[["disease_location"]] <- "None"
p17[["treatment"]]        <- "None"
p17[["cell_category"]]    <- "Myeloid"
p17[["percent.mt"]]       <- PercentageFeatureSet(p17, pattern = "^MT-")
```

---

# 8. P18 – Colon epithelial cohort (PM35158099)

7 patients; each sample loaded from 10X Cellranger output.
Tissue was macroscopically non-inflamed (Inactive).

```{r p18-load}
p18_sample_ids <- c("189", "206", "214", "216", "217", "299", "364")

p18_list <- lapply(p18_sample_ids, function(s) {
  readRDS(file.path(DATA_DIR, paste0("PM35158099/data/", s, "/Seurat.RDS")))
})
p18 <- Reduce(merge, p18_list)
p18[["RNA"]]          <- JoinLayers(p18[["RNA"]])
p18[["cell_category"]]<- "Epithelial"
p18[["sample"]]       <- p18[["patient"]]
```

---

# 9. P19 – Open Targets CD cohort (discovery + replication)

Preprocessed in Python; imported as sparse CSV count matrices with
accompanying metadata files. Split into discovery and replication cohorts.

```{r p19-load}
dis_count <- vroom(file.path(DATA_DIR, "open_target_CD/data/processed_discovery_counts.csv"))
dis_meta  <- read.csv(file.path(DATA_DIR, "open_target_CD/data/processed_discovery_meta.csv"))
dis_genes <- read.csv(file.path(DATA_DIR, "open_target_CD/data/processed_discovery_genes.csv"))
rep_count <- vroom(file.path(DATA_DIR, "open_target_CD/data/processed_replication_counts.csv"))
rep_meta  <- read.csv(file.path(DATA_DIR, "open_target_CD/data/processed_replication_meta.csv"))

build_p19 <- function(count_df, meta_df, genes_df) {
  df <- as.data.frame(count_df)[, -1]
  colnames(df) <- genes_df$X0
  df <- as.data.frame(t(df))
  so <- CreateSeuratObject(counts = df)
  so[["patient"]]          <- meta_df$patient
  so[["sample"]]           <- meta_df$sample
  so[["source"]]           <- meta_df$source
  so[["condition"]]        <- meta_df$condition
  so[["tissue_region"]]    <- meta_df$tissue_region
  so[["disease_location"]] <- meta_df$disease_location
  so[["treatment"]]        <- meta_df$treatment
  so[["cell_category"]]    <- meta_df$cell_category
  so[["cell_type"]]        <- meta_df$cell_type
  so[["percent.mt"]]       <- PercentageFeatureSet(so, pattern = "^MT-")
  so
}

p19_dis <- build_p19(dis_count, dis_meta, dis_genes)
p19_rep <- build_p19(rep_count, rep_meta, dis_genes)
```

---

# 10. Pre-QC visualization

```{r pre-qc-viz}
so_preqc <- Reduce(merge, list(p11, p12, p13, p14, p15, p16, p17, p18, p19_dis, p19_rep))
so_preqc[["RNA"]] <- JoinLayers(so_preqc[["RNA"]])
so_preqc <- SetIdent(so_preqc, value = "source")

# Gene-level filter before visualization (≥0.1% of cells)
counts_preqc          <- GetAssayData(so_preqc, slot = "counts", assay = "RNA")
genes.pct             <- rowMeans(counts_preqc > 0) * 100
so_preqc              <- so_preqc[names(genes.pct[genes.pct > 0.1]), ]

pdf(file.path(OUTPUT_DIR, "merged_cd/plots/unfiltered_qc_vlnplot.pdf"))
print(VlnPlot(so_preqc, features = "nCount_RNA",   pt.size = 0) + NoLegend())
print(VlnPlot(so_preqc, features = "nFeature_RNA", pt.size = 0) + NoLegend())
print(VlnPlot(so_preqc, features = "percent.mt",   pt.size = 0) + NoLegend())
dev.off()
```

---

# 11. Per-dataset QC filtering

QC thresholds were determined by inspecting distribution plots above.
Mitochondrial fraction threshold of ≤25% applied across all datasets.
P13 and P19 QC also applied and saved separately for use in integration.

```{r per-dataset-qc}
p11_qc <- subset(p11, subset = nFeature_RNA > 500 & nFeature_RNA < 2500 &
                               nCount_RNA   > 500 & nCount_RNA   < 20000 & percent.mt <= 25)
p12_qc <- subset(p12, subset = nFeature_RNA > 500 & nFeature_RNA < 3000 &
                               nCount_RNA   > 500 & nCount_RNA   < 25000 & percent.mt <= 25)
p13_qc <- subset(p13, subset = nFeature_RNA > 500 & nFeature_RNA < 3000 &
                               nCount_RNA   > 500 & nCount_RNA   < 15000 & percent.mt <= 25)
p14_qc <- subset(p14, subset = nFeature_RNA > 500 & nFeature_RNA < 2500 &
                               nCount_RNA   > 500 & nCount_RNA   < 20000 & percent.mt <= 25)
p15_qc <- subset(p15, subset = nFeature_RNA > 500 & nFeature_RNA < 2000 &
                               nCount_RNA   > 500 & nCount_RNA   < 15000 & percent.mt <= 25)
p16_qc <- subset(p16, subset = nFeature_RNA > 500 & nFeature_RNA < 3000 &
                               nCount_RNA   > 500 & nCount_RNA   < 20000 & percent.mt <= 25)
p17_qc <- subset(p17, subset = nFeature_RNA > 500 & nFeature_RNA < 3000 &
                               nCount_RNA   > 500 & nCount_RNA   < 15000 & percent.mt <= 25)
p18_qc <- subset(p18, subset = nFeature_RNA > 500 & nFeature_RNA < 4000 &
                               nCount_RNA   > 500 & nCount_RNA   < 40000 & percent.mt <= 25)
p19_dis_qc <- subset(p19_dis, subset = nFeature_RNA > 500 & nFeature_RNA < 4000 &
                                        nCount_RNA   > 500 & nCount_RNA   < 20000 & percent.mt <= 25)
p19_rep_qc <- subset(p19_rep, subset = nFeature_RNA > 500 & nFeature_RNA < 4000 &
                                        nCount_RNA   > 500 & nCount_RNA   < 20000 & percent.mt <= 25)

# Save P13 and P19 QC'd objects for use in 01_cd_atlas_integration.R
saveRDS(p13_qc,    file.path(DATA_DIR, "PM31474370/data/Seurat_qc.RDS"))
saveRDS(p19_dis_qc, file.path(DATA_DIR, "open_target_CD/Seurat_dis_qc.RDS"))
saveRDS(p19_rep_qc, file.path(DATA_DIR, "open_target_CD/Seurat_rep_qc.RDS"))
```

---

# 12. Merge all QC'd datasets

```{r merge}
so_qc <- Reduce(merge, list(p11_qc, p12_qc, p13_qc, p14_qc, p15_qc,
                             p16_qc, p17_qc, p18_qc, p19_dis_qc, p19_rep_qc))
so_qc[["RNA"]] <- JoinLayers(so_qc[["RNA"]])

# Cross-dataset metadata harmonization
so_meta <- so_qc@meta.data %>%
  mutate(
    condition = case_when(
      condition == "CD (NA)" ~ "CD",
      condition == "Healthy" ~ "Control",
      TRUE                   ~ condition
    ),
    tissue_region = case_when(
      tissue_region == "Ileum (terminal)" ~ "Ileum (Terminal)",
      TRUE                                ~ tissue_region
    ),
    disease_location = ifelse(is.na(disease_location), "NA", disease_location),
    cell_category = case_when(
      cell_category == "Epithelial-Enterocyte" ~ "Epithelial",
      cell_category == "Epithelial-Secretory"  ~ "Epithelial",
      TRUE                                     ~ cell_category
    )
  )

so_qc[["condition"]]       <- so_meta$condition
so_qc[["tissue_region"]]   <- so_meta$tissue_region
so_qc[["disease_location"]]<- so_meta$disease_location
so_qc[["cell_category"]]   <- so_meta$cell_category

saveRDS(so_qc, file.path(OUTPUT_DIR, "merged_cd/9p_merge_qc.RDS"))
```

---

# 13. Post-QC visualization

```{r post-qc-viz}
so_qc <- SetIdent(so_qc, value = "source")
pdf(file.path(OUTPUT_DIR, "merged_cd/plots/post_qc_vlnplot.pdf"))
print(VlnPlot(so_qc, features = "nCount_RNA",   pt.size = 0) + NoLegend())
print(VlnPlot(so_qc, features = "nFeature_RNA", pt.size = 0) + NoLegend())
print(VlnPlot(so_qc, features = "percent.mt",   pt.size = 0) + NoLegend())
dev.off()
```

```{r post-qc-metadata-plots}
so_meta <- so_qc@meta.data

pdf(file.path(OUTPUT_DIR, "merged_cd/plots/post_qc_meta.pdf"), width = 6, height = 4)

print(ggplot(so_meta, aes(x = condition, fill = condition)) +
  geom_bar(stat = "count", width = 0.7) +
  ggtitle("Condition") + theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust = 0.5, size = 10)))

print(ggplot(so_meta, aes(x = disease_location, fill = disease_location)) +
  geom_bar(stat = "count", width = 0.7) +
  ggtitle("Disease Location") + theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust = 0.5, size = 10)))

print(ggplot(so_meta, aes(x = tissue_region, fill = tissue_region)) +
  geom_bar(stat = "count", width = 0.7) +
  ggtitle("Tissue Region") + theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust = 0.5, size = 10)))

dev.off()
```
