---
title: "UC Atlas: Dataset Loading, QC, and Pre-integration Merging"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(Seurat)
library(ggplot2)
library(grid)
library(gridExtra)
library(DoubletFinder)
```

# Overview

Loads and prepares all 9 UC datasets (P1–P9) for atlas integration.
Each dataset originates from a different source format and requires
format-specific ingestion before applying unified per-dataset QC thresholds.

After QC, datasets are merged into a single Seurat object and exported
for Harmony integration in `01_atlas_integration.R`.

```{r paths}
BASE_DIR <- "/path/to/uc/scrna"
```

---

# 1. P1 – Smillie et al. (colonoscopy biopsies)

Pre-processed Seurat object; label harmonization applied.

```{r p1-load}
p1 <- readRDS(file.path(BASE_DIR, "p1/Seurat.RDS"))
p1 <- SetIdent(p1, value = "P1")
```

---

# 2. P2 – Parikh et al. (CITE-seq, T/B/Myeloid)

```{r p2-load}
p2 <- readRDS(file.path(BASE_DIR, "p2/Seurat.RDS"))

mapping <- read.csv(file.path(BASE_DIR, "merged/cell_type_mapping.csv"))
p2_label <- mapping$label[match(p2$label, mapping$label_orig)]
p2$label_new <- p2_label
p2 <- subset(p2, subset = label_new != "Discard")
p2 <- SetIdent(p2, value = "label_new")
```

---

# 3. P3 – Kong et al. (colon biopsies)

```{r p3-load}
p3 <- readRDS(file.path(BASE_DIR, "p3/Seurat.RDS"))
p3 <- SetIdent(p3, value = "P3")
```

---

# 4. P4 – Human Gut Cell Atlas (Gut Atlas)

Source: separate epithelial (Epi), immune (Imm), and fibroblast (Fib)
compartment files in Matrix Market format with separate barcodes/genes.

```{r p4-load}
load_mtx_compartment <- function(matrix_path, barcode_path, gene_path, project_id) {
  mat  <- Matrix::readMM(matrix_path)
  bars <- unlist(read.table(barcode_path, sep = "\t", header = FALSE))
  genes <- unlist(read.table(gene_path,  sep = "\t", header = FALSE))
  tab  <- as.data.frame(as.matrix(mat))
  colnames(tab) <- bars
  rownames(tab) <- genes
  CreateSeuratObject(counts = tab, project = project_id)
}

epi_so <- load_mtx_compartment(
  file.path(BASE_DIR, "gut_atlas/epi/gene_sorted-Epi.matrix.mtx"),
  file.path(BASE_DIR, "gut_atlas/epi/Epi.barcodes2.tsv"),
  file.path(BASE_DIR, "gut_atlas/epi/Epi.genes.tsv"), "P4"
)
imm_so <- load_mtx_compartment(
  file.path(BASE_DIR, "gut_atlas/imm/gene_sorted-Imm.matrix.mtx"),
  file.path(BASE_DIR, "gut_atlas/imm/Imm.barcodes2.tsv"),
  file.path(BASE_DIR, "gut_atlas/imm/Imm.genes.tsv"), "P4"
)
fib_so <- load_mtx_compartment(
  file.path(BASE_DIR, "gut_atlas/fib/gene_sorted-Fib.matrix.mtx"),
  file.path(BASE_DIR, "gut_atlas/fib/Fib.barcodes2.tsv"),
  file.path(BASE_DIR, "gut_atlas/fib/Fib.genes.tsv"), "P4"
)
```

```{r p4-meta}
meta_all <- read.table(file.path(BASE_DIR, "gut_atlas/metadata/all.meta2.txt"),
                       sep = "\t", header = TRUE)
meta_all <- meta_all[-1, ]  # drop header duplicate

attach_meta <- function(so, bar_lst) {
  m <- meta_all %>%
    filter(NAME %in% bar_lst) %>%
    select(-c(nGene, nUMI)) %>%
    dplyr::rename(label = Cluster, sample = Sample) %>%
    mutate(condition = case_when(
      Health == "Healthy"      ~ "HC",
      Health == "Inflamed"     ~ "UCI",
      Health == "Non-inflamed" ~ "UCU"
    )) %>%
    select(NAME, sample, condition, label)
  for (col in colnames(m)[-1]) {
    so <- AddMetaData(so, metadata = m[[col]], col.name = col)
  }
  so
}

epi_so <- attach_meta(epi_so, colnames(epi_so))
imm_so <- attach_meta(imm_so, colnames(imm_so))
fib_so <- attach_meta(fib_so, colnames(fib_so))

# Merge across compartments (union of genes)
p4 <- merge(epi_so, list(imm_so, fib_so))
```

---

# 5. P5 – SNAP-seq dataset

```{r p5-load}
p5 <- readRDS(file.path(BASE_DIR, "p5/Seurat.RDS"))
p5 <- SetIdent(p5, value = "P5")
```

---

# 6. P6 – Colon Immune Cell Atlas

Source: sparse count matrix (.mtx) with separate gene and metadata CSVs.

```{r p6-load}
himm <- Matrix::readMM(file.path(BASE_DIR, "imm_atlas/Colon_immune_counts.mtx"))
gene <- read.csv(file.path(BASE_DIR, "imm_atlas/Colon_immune_gene_names.csv"))
meta <- read.csv(file.path(BASE_DIR, "imm_atlas/Colon_immune_metadata.csv"))

meta <- meta %>%
  select(index, donor, region, cell_type) %>%
  dplyr::rename(label = cell_type) %>%
  mutate(sample    = paste(donor, region, sep = "_"),
         condition = "HC") %>%
  select(index, sample, condition, label)

himm_tab <- as.data.frame(t(as.matrix(himm)))
colnames(himm_tab) <- meta$index
rownames(himm_tab) <- gene$index

p6 <- CreateSeuratObject(counts = himm_tab, project = "P6")
for (col in colnames(meta)[-1]) {
  p6 <- AddMetaData(p6, metadata = meta[[col]], col.name = col)
}
```

---

# 7. P7 – Chang et al. (B and T cell atlas)

Source: separate B cell and T cell Seurat objects; Leiden cluster → cell type mapping.

```{r p7-load}
bcell <- UpdateSeuratObject(readRDS(file.path(BASE_DIR, "imm_chang/Exp_Seurat_Bcell_R2.Rds")))
tcell <- UpdateSeuratObject(readRDS(file.path(BASE_DIR, "imm_chang/Exp_Seurat_Tcell_R2.Rds")))

meta_tcell <- as.data.frame(tcell@meta.data) %>%
  mutate(
    label = case_when(
      res.1 %in% c(2,3,5,8,10,11,16) ~ "Naive/memory T",
      res.1 %in% c(7,12,15)          ~ "Gamma delta T",
      res.1 == 14                    ~ "MAIT",
      res.1 == 4                     ~ "T follicular helper",
      res.1 == 6                     ~ "T reg",
      res.1 %in% c(0,1,9,13)        ~ "CD8 resident memory T"
    ),
    condition = case_when(
      disease_assignment == 1 ~ "HC",
      disease_assignment == 2 ~ "UCA"
    )
  ) %>%
  dplyr::rename(sample = sample_gp) %>%
  select(sample, condition, label)

meta_bcell <- as.data.frame(bcell@meta.data) %>%
  mutate(
    label = case_when(
      res.1 %in% c(2,7,8)              ~ "Naive B",
      res.1 %in% c(1,3,4)              ~ "Memory B",
      res.1 %in% c(0,5,6,9:16)        ~ "Plasma B"
    ),
    condition = case_when(
      disease_assignment == 1 ~ "HC",
      disease_assignment == 2 ~ "UCA"
    )
  ) %>%
  dplyr::rename(sample = sample_gp) %>%
  select(sample, condition, label)

tcell_so <- CreateSeuratObject(counts = as.data.frame(tcell@assays$RNA@counts), project = "P7")
bcell_so <- CreateSeuratObject(counts = as.data.frame(bcell@assays$RNA@counts), project = "P7")

for (col in colnames(meta_tcell)) tcell_so <- AddMetaData(tcell_so, meta_tcell[[col]], col.name = col)
for (col in colnames(meta_bcell)) bcell_so <- AddMetaData(bcell_so, meta_bcell[[col]], col.name = col)

p7 <- merge(bcell_so, tcell_so)
```

---

# 8. P8 – Internal dataset (Dulai lab)

Cluster-to-label mapping applied to integrate with atlas nomenclature.

```{r p8-load}
internal <- readRDS(file.path(BASE_DIR, "p8/Integrated_naive_nr_r_2023.rds"))
internal_counts <- as.data.frame(internal@assays$RNA@counts)
p8 <- CreateSeuratObject(counts = internal_counts, project = "P8")

internal_meta <- internal@meta.data %>%
  select(identity, seurat_clusters) %>%
  mutate(
    condition = "Inflamed",
    sample    = identity,
    label = case_when(
      seurat_clusters == 0  ~ "CD8+ T",
      seurat_clusters == 1  ~ "Fibroblast",
      seurat_clusters == 2  ~ "Macrophage",
      seurat_clusters %in% c(3,7,9,13) ~ "Plasma",
      seurat_clusters == 4  ~ "Neutrophil",
      seurat_clusters == 5  ~ "Naive/Memory B",
      seurat_clusters == 6  ~ "Absorptive epithelial",
      seurat_clusters == 8  ~ "Secretory epithelial",
      seurat_clusters == 10 ~ "Endothelial",
      seurat_clusters %in% c(11,12,16,18,20) ~ "Fibroblast",
      seurat_clusters == 15 ~ "Secretory epithelial",
      seurat_clusters == 17 ~ "Mast",
      seurat_clusters == 19 ~ "Secretory epithelial",
      seurat_clusters %in% c(14,21,22) ~ "Discard"
    ),
    label_category = case_when(
      seurat_clusters == 0  ~ "T",
      seurat_clusters %in% c(1,11,12,16,18,20) ~ "Mesenchymal",
      seurat_clusters %in% c(2,4,17) ~ "Myeloid",
      seurat_clusters %in% c(3,5,7,9,13,21) ~ "B",
      seurat_clusters %in% c(6,8,15,19) ~ "Epithelial",
      seurat_clusters == 10 ~ "Endothelial",
      seurat_clusters %in% c(14,22) ~ "Discard"
    )
  ) %>%
  select(sample, condition, label, label_category)

for (col in colnames(internal_meta)) {
  p8 <- AddMetaData(p8, internal_meta[[col]], col.name = col)
}
p8 <- subset(p8, subset = label_category != "Discard")
```

---

# 9. P9 – Internal raw 10X data (Healthy + Inflamed)

```{r p9-load}
load_10x <- function(data_dir) {
  CreateSeuratObject(counts = Read10X(data.dir = data_dir))
}

edit_meta <- function(so, sample_id, condition_val) {
  so@meta.data[["orig.ident"]]     <- "P9"
  so@meta.data[["condition"]]      <- condition_val
  so@meta.data[["sample"]]         <- sample_id
  so@meta.data[["label"]]          <- "Unassigned"
  so@meta.data[["label_category"]] <- "Unassigned"
  so
}

# Healthy donors
hc1_so <- edit_meta(load_10x(file.path(BASE_DIR, "p9/hc1/Filtered")), "hc1", "Healthy")
hc2_so <- edit_meta(load_10x(file.path(BASE_DIR, "p9/hc2/Filtered")), "hc2", "Healthy")
hc3_so <- edit_meta(load_10x(file.path(BASE_DIR, "p9/hc3/Filtered")), "hc3", "Healthy")
hc7_so <- edit_meta(load_10x(file.path(BASE_DIR, "p9/hc7/Filtered")), "hc7", "Healthy")
hc8_so <- edit_meta(load_10x(file.path(BASE_DIR, "p9/hc8/Filtered")), "hc8", "Healthy")

# Inflamed donors
inf3_so <- edit_meta(load_10x(file.path(BASE_DIR, "p9/inf3/filtered")), "inf3", "Inflamed")
inf5_so <- edit_meta(load_10x(file.path(BASE_DIR, "p9/inf5/Filtered")), "inf5", "Inflamed")
inf6_so <- edit_meta(load_10x(file.path(BASE_DIR, "p9/inf6/Filtered")), "inf6", "Inflamed")
inf9_so <- edit_meta(load_10x(file.path(BASE_DIR, "p9/inf9/Filtered")), "inf9", "Inflamed")

p9 <- Reduce(merge, list(hc1_so, hc2_so, hc3_so, hc7_so, hc8_so,
                         inf3_so, inf5_so, inf6_so, inf9_so))
p9 <- SetIdent(p9, value = "orig.ident")
```

---

# 10. Merge all datasets

```{r merge-all}
# Merge P1–P7 external datasets with P8–P9 internal
so_all <- Reduce(merge, list(p1, p2, p3, p4, p5, p6, p7, p8, p9))
so_all$orig.ident <- as.character(so_all@active.ident)
```

---

# 11. Per-dataset QC filtering

QC thresholds were set per dataset by inspecting nCount_RNA, nFeature_RNA,
and mitochondrial fraction distributions. Thresholds reflect dataset-specific
library preparation and sequencing depth.

```{r calc-pct-mt}
so_all[["percent_mt"]] <- PercentageFeatureSet(so_all, "^MT-")
```

```{r qc-violin-before}
VlnPlot(so_all, features = "nCount_RNA",   pt.size = 0, group.by = "orig.ident")
VlnPlot(so_all, features = "nFeature_RNA", pt.size = 0, group.by = "orig.ident")
VlnPlot(so_all, features = "percent_mt",   pt.size = 0, group.by = "orig.ident")
```

```{r qc-density-before}
meta <- so_all@meta.data %>%
  dplyr::rename(paper = orig.ident, nUMI = nCount_RNA, nGene = nFeature_RNA)

meta %>%
  ggplot(aes(color = paper, x = nUMI, fill = paper)) +
  geom_density(alpha = 0.2) + scale_x_log10() + theme_classic() +
  ylab("Cell density") + ggtitle("UMI distribution by dataset")

meta %>%
  ggplot(aes(color = paper, x = nGene, fill = paper)) +
  geom_density(alpha = 0.2) + scale_x_log10() + theme_classic() +
  ggtitle("Gene count distribution by dataset")

meta %>%
  ggplot(aes(color = paper, x = percent_mt, fill = paper)) +
  geom_density(alpha = 0.2) + theme_classic() +
  ggtitle("Mitochondrial fraction by dataset")
```

```{r per-dataset-subset}
sub_p1 <- subset(so_all, subset = orig.ident == "P1")
sub_p2 <- subset(so_all, subset = orig.ident == "P2")
sub_p3 <- subset(so_all, subset = orig.ident == "P3")
sub_p4 <- subset(so_all, subset = orig.ident == "P4")
sub_p5 <- subset(so_all, subset = orig.ident == "P5")
sub_p6 <- subset(so_all, subset = orig.ident == "P6")
sub_p7 <- subset(so_all, subset = orig.ident == "P7")
sub_p8 <- subset(so_all, subset = orig.ident == "P8")
sub_p9 <- subset(so_all, subset = orig.ident == "P9")
```

```{r per-dataset-qc-filter}
# Per-dataset thresholds informed by distribution inspection above
filtered_p1 <- subset(sub_p1, subset = nCount_RNA >= 500  & nCount_RNA <= 20000 &
                                        nFeature_RNA >= 500  & nFeature_RNA <= 2500 &
                                        percent_mt < 20)
filtered_p2 <- subset(sub_p2, subset = nCount_RNA >= 500  & nCount_RNA <= 10000 &
                                        nFeature_RNA >= 250  & nFeature_RNA <= 3000 &
                                        percent_mt < 15)
filtered_p3 <- subset(sub_p3, subset = nCount_RNA >= 500  & nCount_RNA <= 25000 &
                                        nFeature_RNA >= 200  & nFeature_RNA <= 4000 &
                                        percent_mt < 20)
filtered_p4 <- subset(sub_p4, subset = nCount_RNA >= 500  & nCount_RNA <= 20000 &
                                        nFeature_RNA >= 250  & nFeature_RNA <= 3000 &
                                        percent_mt < 20)
filtered_p5 <- subset(sub_p5, subset = nCount_RNA >= 500  & nCount_RNA <= 10000 &
                                        nFeature_RNA >= 200  & nFeature_RNA <= 2500 &
                                        percent_mt < 15)
filtered_p6 <- subset(sub_p6, subset = nCount_RNA >= 500  & nCount_RNA <= 30000 &
                                        nFeature_RNA >= 700  & nFeature_RNA <= 3000 &
                                        percent_mt < 15)
filtered_p7 <- subset(sub_p7, subset = nCount_RNA >= 500  & nCount_RNA <= 10000 &
                                        nFeature_RNA >= 400  & nFeature_RNA <= 2500 &
                                        percent_mt < 10)
filtered_p8 <- subset(sub_p8, subset = nCount_RNA >= 500  & nCount_RNA <= 40000 &
                                        nFeature_RNA >= 250  & nFeature_RNA <= 6000 &
                                        percent_mt < 20)
filtered_p9 <- subset(sub_p9, subset = nCount_RNA >= 500  & nCount_RNA <= 25000 &
                                        nFeature_RNA >= 250  & nFeature_RNA <= 3500 &
                                        percent_mt < 20)
```

---

# 12. Gene-level filtering and DoubletFinder (P2–P7)

Genes expressed in fewer than 10 cells per dataset are removed before
doublet detection. DoubletFinder is applied to re-processed external
datasets (P2–P7) where per-sample isolation was performed.

```{r gene-filter-fn}
gene_filter <- function(so) {
  counts   <- GetAssayData(so, slot = "counts")
  nonzero  <- counts > 0
  keep     <- Matrix::rowSums(nonzero) >= 10
  CreateSeuratObject(counts[keep, ], meta.data = so@meta.data)
}

filtered_p2 <- gene_filter(filtered_p2)
filtered_p3 <- gene_filter(filtered_p3)
filtered_p4 <- gene_filter(filtered_p4)
filtered_p5 <- gene_filter(filtered_p5)
filtered_p6 <- gene_filter(filtered_p6)
filtered_p7 <- gene_filter(filtered_p7)
```

```{r doublet-finder-prep}
prep_doublet_finder <- function(so) {
  so <- NormalizeData(so)
  so <- FindVariableFeatures(so, verbose = FALSE)
  so <- ScaleData(so, vars.to.regress = c("nFeature_RNA", "percent_mt"), verbose = FALSE)
  so <- RunPCA(so, npcs = 20, verbose = FALSE)
  so <- RunUMAP(so, dims = 1:10, verbose = FALSE)
  so
}

filtered_p2 <- prep_doublet_finder(filtered_p2)
filtered_p3 <- prep_doublet_finder(filtered_p3)
filtered_p4 <- prep_doublet_finder(filtered_p4)
filtered_p5 <- prep_doublet_finder(filtered_p5)
filtered_p6 <- prep_doublet_finder(filtered_p6)
filtered_p7 <- prep_doublet_finder(filtered_p7)
```

```{r doublet-finder-pk}
find_pk <- function(so) {
  sweep.res <- paramSweep_v3(so, sct = FALSE, PCs = 1:10)
  sweep.stats <- summarizeSweep(sweep.res, GT = FALSE)
  bcmvn <- find.pK(sweep.stats)
  pK <- as.numeric(as.character(bcmvn$pK))
  pK[which(bcmvn$BCmetric == max(bcmvn$BCmetric))]
}

pk_p2 <- find_pk(filtered_p2)
pk_p3 <- find_pk(filtered_p3)
pk_p4 <- find_pk(filtered_p4)
pk_p5 <- find_pk(filtered_p5)
pk_p6 <- find_pk(filtered_p6)
pk_p7 <- find_pk(filtered_p7)
```

```{r doublet-finder-run}
# Expected doublet rates based on 10X Genomics loading density estimates
run_doublet_finder <- function(so, pct_exp, pk) {
  nExp <- round(ncol(so) * pct_exp)
  doubletFinder_v3(so, pN = 0.25, pK = pk, nExp = nExp, PCs = 1:10)
}

filtered_p2 <- run_doublet_finder(filtered_p2, 0.035, pk_p2)
filtered_p3 <- run_doublet_finder(filtered_p3, 0.035, pk_p3)
filtered_p4 <- run_doublet_finder(filtered_p4, 0.028, pk_p4)
filtered_p5 <- run_doublet_finder(filtered_p5, 0.031, pk_p5)
filtered_p6 <- run_doublet_finder(filtered_p6, 0.016, pk_p6)
filtered_p7 <- run_doublet_finder(filtered_p7, 0.080, pk_p7)
```

---

# 13. Merge filtered datasets and harmonize sample names

```{r final-merge}
filtered <- Reduce(merge, list(
  filtered_p1, filtered_p2, filtered_p3, filtered_p4,
  filtered_p5, filtered_p6, filtered_p7, filtered_p8, filtered_p9
))

# Gene-level filter on merged object: keep genes in ≥ 50 cells
counts   <- GetAssayData(filtered, slot = "counts")
keep     <- Matrix::rowSums(counts > 0) >= 50
filtered <- subset(filtered, features = rownames(counts)[keep])
```

```{r sample-name-harmonize}
# Standardize sample identifiers to dataset_#_sampleID format
filtered_meta <- filtered@meta.data %>%
  mutate(sample = case_when(
    # P8 internal patients (anonymized)
    sample == "patient_alpha" ~ "P8_#_patient_alpha",
    sample == "patient_beta"  ~ "P8_#_patient_beta",
    sample == "patient_gamma" ~ "P8_#_patient_gamma",
    sample == "patient_delta" ~ "P8_#_patient_delta",
    sample == "patient_w"     ~ "P8_#_patient_w",
    sample == "patient_x"     ~ "P8_#_patient_x",
    sample == "patient_y"     ~ "P8_#_patient_y",
    sample == "patient_z"     ~ "P8_#_patient_z",
    sample == "patient_A"     ~ "P8_#_patient_A",
    sample == "patient_B"     ~ "P8_#_patient_B",
    sample == "patient_C"     ~ "P8_#_patient_C",
    sample == "patient_D"     ~ "P8_#_patient_D",
    # P9 samples
    sample == "hc1"  ~ "P9_#_hc1",
    sample == "hc2"  ~ "P9_#_hc2",
    sample == "hc3"  ~ "P9_#_hc3",
    sample == "hc7"  ~ "P9_#_hc7",
    sample == "hc8"  ~ "P9_#_hc8",
    sample == "inf3" ~ "P9_#_inf3",
    sample == "inf5" ~ "P9_#_inf5",
    sample == "inf6" ~ "P9_#_inf6",
    sample == "inf9" ~ "P9_#_inf9",
    TRUE ~ sample
  ))
filtered@meta.data <- filtered_meta
```

```{r save-filtered}
saveRDS(filtered, file.path(BASE_DIR, "merged/Seurat_filtered_9p.RDS"))
```

---

# 14. Post-filter QC visualization

```{r qc-violin-after}
VlnPlot(filtered, features = "nCount_RNA",   pt.size = 0, group.by = "orig.ident")
VlnPlot(filtered, features = "nFeature_RNA", pt.size = 0, group.by = "orig.ident")
VlnPlot(filtered, features = "percent_mt",   pt.size = 0, group.by = "orig.ident")
```

---

# 15. Per-dataset UMAP validation (post-integration)

After running `01_atlas_integration.R`, load the integrated object and
verify that each dataset contributes expected cell types.

```{r per-dataset-umap}
# Load integrated object (output of 01_atlas_integration.R)
so_integ <- readRDS(file.path(BASE_DIR, "merged/Seurat_merged_notfiltered_transformed.RDS"))
so_integ <- subset(so_integ,
  subset = label %in% c("B_discard", "T_discard", "Epithelial_discard", "Discard"),
  invert = TRUE
)
so_integ <- NormalizeData(so_integ)
so_integ <- FindVariableFeatures(so_integ)
so_integ <- ScaleData(so_integ)
so_integ <- RunPCA(so_integ, verbose = FALSE)
so_integ <- RunUMAP(so_integ, reduction = "pca", dims = 1:30)
```

```{r umap-by-dataset}
# Per-dataset UMAPs: check cell type composition and batch effects
datasets <- paste0("P", 1:9)
for (ds in datasets) {
  sub <- subset(so_integ, subset = orig.ident == ds)
  print(
    DimPlot(sub, reduction = "umap", raster = FALSE, label = TRUE, repel = TRUE) +
      ggtitle(ds) + theme(legend.position = "none")
  )
}
```

```{r umap-overall}
# Atlas-level UMAP colored by dataset and cell type label
DimPlot(so_integ, group.by = "orig.ident", raster = FALSE) +
  ggtitle("All datasets")

DimPlot(so_integ, group.by = "label", raster = FALSE,
        label = TRUE, repel = TRUE) +
  theme(legend.position = "none") +
  ggtitle("Cell type labels")
```
